Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
[A-10] In page 5 (right column), I think that the text "The ESBMC ... (2015)" is unclear and it should be rewritten. Beside, why do you use a "transposed incidence matrix" and "identity matrix"? (maybe is it related to eq. 4??).

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints

@@

$P$ is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}

@@

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}

@@

The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}. Both use slack variables in order to eliminate the modulus operator of Eq.~\ref{hw-sw-partitioning} and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.

@@

The ESBMC algorithm starts with the declarations of hardware, software, and communication costs. $S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\ref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB. Here, matrices $A$ and $b$ are generated. At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.

@@

In the ESBMC algorithm is not necessary to add slack variables at Eq.~\ref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.

@@

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one instructs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that 
meets the constraints, then the \textit{Fobj} value is provided.

>>>>

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints

@@

$P$ is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}. The hardware cost of $P$ is given by Eq.~\eqref{hardware-costs}

@@

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\eqref{software-communication-costs}

@@

The ILP and GA were taken from our previous studies, from~\cite{Trindade2015} and~\cite{Trindade2016}. Both use slack variables in order to eliminate the modulus operator of Eq.~\eqref{hw-sw-partitioning} and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB, as shown in~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.

@@

The ESBMC algorithm starts with the declarations of hardware, software, and communication costs. $S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB. Here, matrices $A$ and $b$ are generated. At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.

@@

In the ESBMC algorithm is not necessary to add slack variables at Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.

@@

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\eqref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one instructs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that 
meets the constraints, then the \textit{Fobj} value is provided.
